|

### 2025-05-23 doc/paper.qmd
table rendered

@@

@@

```{r}
#| label: fig-gapminder2007_plot
#| fig-cap: "Gapminder 2007: Life Expectancy vs. GDP per Capita"
#| echo: false
#| fig-align: center
knitr::include_graphics("../output/gapminder_figure.png")
```

@@

This section compares the static 2007 snapshot with Gapminder’s dynamic global development chart @fig-gapminder_original [@gapminder_health_chart].
```{r}
#| label: fig-gapminder_original
#| fig-cap: "Original World Health Chart 2021 from Gapminder Foundation"
#| echo: false
#| fig-align: center
knitr::include_graphics("countries_health_wealth_2021.pdf")
```

>>>>

```{python}
#| echo: false
#| output: false

import pickle
import pandas as pd

# Load the prepared summary table
with open('../output/summary_statistics.pickle', 'rb') as f:
    summary = pickle.load(f)

# Clean column names for LaTeX rendering
def escape_special_characters(df):
    df.columns = [col.replace('_', '\\_').replace('#', '\\#') for col in df.columns]
    return df

# Formatting for float values
def custom_float_format(x):
    return f"{x:.2f}" if pd.notnull(x) else ""

# Function to prep LaTeX table
def prep_latex_table(df, caption=None, label=None):
    df = escape_special_characters(df.reset_index(drop=True))
    num_columns = len(df.columns)
    column_format = 'l' + 'r' * (num_columns - 1)
    latex_table = df.to_latex(
        column_format=column_format,
        index=False,
        float_format=custom_float_format,
    )
    latex_table_lines = [
        "\\begin{table}",
        "\\centering",
        "\\resizebox{\\textwidth}{!}{%",
        latex_table,
        "}",
        f"\\caption{{{caption}}}" if caption else "",
        f"\\label{{{label}}}" if label else "",
        "\\end{table}"
    ]
    return "\n".join(line for line in latex_table_lines if line)
```

@@

```{python}
#| label: tbl-gapminder2007_summary
#| tbl-cap: "Summary Statistics by Continent (Gapminder 2007)"
#| echo: false
#| output: asis

print(prep_latex_table(summary))
print("\n\\caption*{\\textnormal{This table reports the mean and median life expectancy and GDP per capita, along with the total population and number of countries per continent for the year 2007.}}")
```

@@

```{python}
#| label: fig-gapminder2007_plot
#| fig-cap: "Gapminder 2007: Life Expectancy vs. GDP per Capita"
#| echo: false

from IPython.display import Image
Image(filename="../output/gapminder_figure.png")
```

Together, these outputs provide a clear and interpretable overview of global development disparities, offering insights into how income and health outcomes align across continents at a given point in time.

@@

This section compares the static 2007 snapshot with Gapminder’s dynamic global development chart @fig-gapminder_original [@gapminder_health_chart].
```{python}
#| label: fig-gapminder_original
#| fig-cap: "Original World Health Chart 2021 from Gapminder Foundation"
#| echo: false

from IPython.display import Image
Image(filename="countries_health_wealth_2021-1.png")
```
